Large and Infinitary Quotient Inductive-Inductive Types

### 2020-01-10 draft/paper.tex
rename metavars

Algebraic notions of models of type theories are examples for this. Here,
initial models represent syntax, and initiality corresponds to induction on
syntax. Several variants have been used, from contextual categories \cite{gat}
and comprehension categories \cite{jacobs1993comprehension} to categories with
families \cite{Dybjer96internaltype} (CwF).
%
Whereas the initial category can be given by first defining the type
of objects (the empty type) and then defining morphisms as a separate
inductive family, for the initial CwF one has to define $Ob$, $Mor$
and two extra sorts $Ty$ and $Tm$ \emph{inductive-inductively}, at the
same time. This is because there is a constructor of $Ob$ which refers
to $Ty$, constructors of $Ty$ refer to $Ob$ and $Sub$, and so on. This
is illustrated by the following excerpt of the signature for CwFs
extending the above signature for categories.
\begin{alignat*}{3}
  & Ty && : Ob\ra \U \\
  & empty  && : Ob \\
  & ext && : (\Gamma:Ob)\ra Ty\,\Gamma\ra Ob \\
  & \blank[\blank] && : Ty\,\Delta\ra Mor\,\Gamma\,\Delta\ra Ty\,\Gamma
\end{alignat*}

>>>>

Algebraic notions of models of type theories are examples for this. Here,
initial models represent syntax, and initiality corresponds to induction on
syntax. Several variants have been used, from contextual categories \cite{gat}
and comprehension categories \cite{jacobs1993comprehension} to categories with
families \cite{Dybjer96internaltype} (CwF).
%
Whereas the initial category can be given by first defining the type
of objects (the empty type) and then defining morphisms as a separate
inductive family, for the initial CwF one has to define $Ob$, $Mor$
and two extra sorts $Ty$ and $Tm$ \emph{inductive-inductively}, at the
same time. This is because there is a constructor of $Ob$ which refers
to $Ty$, constructors of $Ty$ refer to $Ob$ and $Sub$, and so on. This
is illustrated by the following excerpt of the signature for CwFs
extending the above signature for categories.
\begin{alignat*}{3}
  & Ty && : Ob\ra \U \\
  & empty  && : Ob \\
  & ext && : (I:Ob)\ra Ty\,I\ra Ob \\
  & \blank[\blank] && : Ty\,J\ra Mor\,I\,J\ra Ty\,I
\end{alignat*}
